\documentclass[]{article}

%opening
\title{Constitution of The High Council of Tonys}
\author{Constitutional Committee of the High Council}

\begin{document}
	
\maketitle



\begin{abstract}
	This document exists to outline the makeup and rules of the High Council of Tonys. The High Council of Tonys shall be hereby referred to as the High Council, the Council, the HC, and the HCoT. The members of the HCoT who will be listed in section \ref{sec:members} will be hereby referred to as the Members, and the Tonys.
\end{abstract}

\newpage
\tableofcontents

\newpage
\section{Members}
\label{sec:members}
	This order of this list reflects absolutely nothing. The names are randomly distributed at compile time. The position of a council member's title has no effect on their position on the council.
	\subsection{Council Member George Kush}
	\label{subsec:corbett}
		Corbett Kurtz
	\subsection{Council Member Mackerel Bucket}
	\label{subsec:hunter}
		Hunter Noel
	\subsection{Council Member Redskin}
	\label{subsec:dhalton}
		Dhalton Akey
	\subsection{Council Member Sax Man}
	\label{subsec:garrett}
		Garrett Shirley
	\subsection{Council Member Pylot}
	\label{subsec:jon}
		Jonathan Boos
	\subsection{Council Member Spooky Bones}
	\label{subsec:tyler}
		Tyler A.
	\subsection{Council Member Hew}
	\label{subsec:matt}
		Matthew Brown
	\subsection{Council Member "what?"}
	\label{subsec:gary}
		Garret Andersen
	\subsection{Council Member Walrus}
	\label{subsec:travis}
		Travis Wallace
	\subsection{Council Member Chode}
	\label{subsec:adam}
		Adam Ferla
	
\newpage
\section{Rules of Conduct}
\label{sec:rulesConduct}

\subsection{Rule 1}
Members shall give out all personal information.

\subsection{Rule 2}
Members shall not be a cry baby bitch.

\subsection{Rule 3}
Members shall not believe themselves to be hot shit.
\subsubsection{\textit{Hot Shit Rule}}
A member cannot be hot shit by their own opinion, the status of a members shit temperature shall be determined by the rest of the council.

\subsection{Rule 4}
Members shall grow up.

\subsection{Rule 5}
A members personal business is everyone's business

\subsection{Rule 6}
All rights to those who council members talk to are under the council's control.

\subsection{Rule 7}
All those who say eat a dick Ricardo Jr. shall also eat dicks.

\subsection{Rule 8}
Those members who use God's name in vain shall aquire no pussy of the night the name is taken in vain.

\subsection{Rule 9}
Those members who keep quiet shall remain quiet until further spoken to.

\subsection{Rule 10}
Those members who declare other council members to have a good weekend shall not have a good weekend because that is gay shit.
\subsubsection{\textit{Gay Shit Rule}}
Without prior permission from the council all members are obliged to do whatever is in their power to "be missed with that gay shit". Failure to miss gay shit is gay shit which as previously stated all members are obliged to miss.

\subsection{Rule 11}
Those members who ghost the council never really leave the council for that member has no friends outside of the council.

\subsection{Rule 12}
Those members who have friends outside of the council shall be burdened with the wookie of a female partner.

\subsection{Rule 13}
A member who has a problem with another member or members of the council is every high member of the councils problem.
\subsubsection{\textit{High Members of the Council}}
The High Members of the Council referred to hereby as the HMoC or the High Members will be detailed in section \ref{subsec:highMemebers}.

\subsection{Rule 14}
Those members who throw hands with other council members will be looked down upon by the other council members as this is a council and those who resort to such violence are rather sensitive and do not understand a quality roast. The shit a member has brought upon themselves through the course of their actions and words does not put them above a quality roast, and to think so is to act childish and to act better than the council members.
\subsubsection{\textit{Equality of Members}}
All members of the council regardless of their position(s) within the council are equally shitty. 

\subsection{Rule 15}
A member who says "I was not fuck tard and I lettered" are angry for something that is entirely their own fault and shall take a knee.

\subsection{Rule 16}
A member who uses another council member(s) against another member(s) will be looked down upon by the Toniest of all Gods for that is not the way of the Council.

\newpage
\section{Rules of Operation}
\label{sec:rulesOperation}
This section will detail the operations of the council as they are added.

\subsection{Ratification}
The constitution will be ratified whenever there is a change or addition to it. It will be ratified by a vote of the members as detailed in section \ref{subsec:voting}. Ratification will require at least 50\% of the members to vote in favor of ratification.
\subsubsection{\textit{Changes Exempt From Full Ratification}}
Grammatical corrections, clarifications, and name changes will not require a full ratification of the updated constitution provided they do not change the meaning, interpretation, or usage of the constitution.

\subsection{Voting}
\label{subsec:voting}
Voting on matters by the council will be done as follows. The council will use the voting functionality provided by group me to vote on matters. The vote will be initiated by the council chair.
\newpage
\section{Current Status of the Council}
\label{sec:status}
This section will be updated as the state of the Council changes.

\subsection{Council Chair}
The current Council Chair is Council Member Porcelain Tub, following his appointment by Council Member Redskin at the creation of the council and following a vote of confidence that was initiated by Council Member Sax Man at the end of the creation period of the council.

\section{Pacts and Agreements}
\label{sec:pacts}
This section will contain all pacts and agreements that all current council members are sworn to.
Failure to live up to one of these agreements is grounds for expulsion from the council.

\subsection{Dementia Fight Club}
\label{subsec:pacts:dementia}
Can't talk about fight club if you don't remember fight club.

\subsubsection{Pact}
\label{subsubsec:pacts:dementia:pac}
If at least two (\textbf{2}) members of the council are deemed to have dementia the other council members are to organize a fight club consisting of the two dementia afflicted individuals.
The individuals must fit the definition of dementia that is in section \ref{subsubsec:pacts:dementia:stips} or the majority of the living council members agree that an individual is sun-downing before noon. Under those circumstances a council member will be deemed to have dementia.

\subsubsection{Stipulations}
\label{subsubsec:pacts:dementia:stips}
\begin{enumerate}
	\item \textbf{Two} people must have dementia for this pact to take effect. 

	\item \noindent \textit{Dementia} is to be defined as follows: If a council member does not remember something they were told within at least 12 hours.
	Exceptions include if the individual is under the excessive influence of substances that shall not be named nor limited.
\end{enumerate}

\end{document}
